---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(dplyr)  
library(ggplot2)
```
### Sumarry of the data collected:
- **The minimum number of passengers** calculates the lowest amount of passanges on a bus
- **The maximum number of passengers** calculates the highest amount of passengers on a bus
- **The mean number of passengers** calculates the average amount of passengers on a bus

```{css}
body {
  background-color: grey;
  color: lightblue;
}

```
## Bus Data with graphs for distribution of time and passangers

I am analyzing the number of passengers and the time on bus 195 that starts from stop C Alfred street near Britomart. I want to see if there are more people on certain times.

```{r}
# Load the data from a CSV file
data_bus <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vSqrIPrbtbUdOxqxFJFzLIGmbZy83YVRMlIFe4z7qtOEqCt6eF77PanjZcQ8eAnPZQChhvduTIC0lYg/pub?output=csv"
logged_data <- read.csv(data_bus)

# Renaming the columns for clarity
latest_data <- logged_data %>%
  rename(
    bus_time = names(logged_data)[2], 
    num_passengers = names(logged_data)[3],  
    travel_reason = names(logged_data)[4]  
  )

# Summary calculations for passengers
num_passengers_summary <- latest_data %>%
  summarise(
    min_passengers_recorded = min(num_passengers, na.rm = TRUE),
    max_passengers_recorded = max(num_passengers, na.rm = TRUE),
    average_passengers_recorded = mean(num_passengers, na.rm = TRUE)
  )

# Summary calculations for bus times
bus_time_summary <- latest_data %>%
  summarise(
    min_bus_time = min(bus_time, na.rm = TRUE),
    max_bus_time = max(bus_time, na.rm = TRUE),
    average_bus_time = mean(bus_time, na.rm = TRUE)
  )
```

```{r}
#graphs for bus times
ggplot(latest_data, aes(x = bus_time)) +
  geom_bar(fill = "skyblue", color = "grey", alpha = 0.8) +
  labs(
    title = "Distribution of Bus Times Recorded",
    x = "Bus Time", 
    y = "Frequency"
  )

```

```{r}
#graphs for passengers
ggplot(latest_data, aes(x = num_passengers)) +
  geom_bar(fill = "skyblue", color = "grey", alpha = 0.8) +
  labs (
    title = "Distribution of the Number of Passengers on Bus 195 from Stop C, Alfred Street Near Britomart",
    x = "Number of Passengers",
    y = "Count of Responses"
  )
```

## Summary of the Data collected

- `r paste("The minimum number of passengers recorded is", num_passengers_summary$min_passengers_recorded, 
          ". The maximum number of passengers recorded is", num_passengers_summary$max_passengers_recorded, 
          ". The average number of passengers recorded is", round(num_passengers_summary$average_passengers_recorded, 1))`

- `r paste("The earliest recorded bus time is", bus_time_summary$min_bus_time, 
          ". The latest recorded bus time is", bus_time_summary$max_bus_time, 
          ". The average bus time is", round(bus_time_summary$average_bus_time, 1))`
